\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-12-14 Manuscript/Manuscript.tex
added more exlplanations to each model

The correlation and regression analysis approach of statistical research on bicycle lanes is used to establish significant relationships amongst variables. In \citet{1MateoBabiano2016}, the approach using Spearman's correlation coefficient rho was used, which was suitable because the variables deviated from a normal distribution. The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution. The results of the Spearman correlation of station usage and infrastructure type can be seen in ~\ref{table:MB}, where shred pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage. \par
Other analyses used include Differences-in-Differences, Pearson's R correlation coefficient, Panel regressions, and Counterfactual based on control \cite{Karpinski2021}. These were used when the data being analyzed was usership of Boston's bike share program before and after the addition of bike lanes.

@@

@@

In the group of papers addressed, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}.

>>>>

The correlation and regression analysis approach of statistical research on bicycle lanes is used to establish significant relationships amongst variables. In \citet{1MateoBabiano2016}, the approach using Spearman's correlation coefficient rho was used, which was suitable because the variables deviated from a normal distribution. The variables used were Public bicycle-sharing programs (PBSP) station usage frequency and length of bike-ways, which do not follow a normal distribution. The results of the Spearman correlation of station usage and infrastructure type can be seen in Table ~\ref{table:MB}, where shared pathways, bicycle paths, connections, and separated pathways were shown to have a significant impact on PBSP usage. \par
Other analyses used include Differences-in-Differences, Pearson's R correlation coefficient, Panel regressions, and Counterfactual based on control \cite{Karpinski2021}. These were used when the data being analyzed was usership of Boston's bike share program before and after the addition of bike lanes.

@@

While a fairly simple technique, basic regression and correlation analyses are a fundamental statistical tools offering multiple advantages in data exploration and analysis. These techniques  allow for the understanding and quantification of relationships between variables. Regression analysis not only reveals the nature and strength of connections between dependent and independent variables, but also aids in prediction and model interpretation. It serves as a basis for decision-making by allowing insights into influential data points, model comparison, and assumption checking. Similarly, correlation analysis succinctly measures the degree and direction of association between two  variables, which gives a simple but effective way to summarizing their relationship \cite{Bewick_Cheek_Ball_2003}. All in all, these basic analyses provide crucial foundations for further statistical modeling, making them indispensable in the field of what variable affecting cycling will provide the greatest increase in bike share usage. Even though it is a simple technique, we are able to tell that there is a significant relationship between shared pathways, bicycle paths and separated pathways on the amount of bike share station usage. Which provides a solid foundation of evidence on how to improve cycling infrastructure in urban areas.

@@

In the group of papers addressed, the multinomial logit (MNL) model was used to estimate the travel choice of bicycle for commuting \cite{10Zhao2013}. Multilevel models, unlike traditional regression approaches, offer several crucial advantages. Firstly, they accurately handle hierarchical data structures, avoiding underestimation of standard errors and overstating statistical significance by recognizing and accounting for group-level variability. Secondly, these models address substantive inquiries related to group effects, crucial in scenarios like transportation mode to work choices or identifying 'outlying' groups, providing insights into value-added effects at different levels. Thirdly, they enable simultaneous estimation of group effects and group-level predictors without confounding their impacts, which can't be separated in fixed effects models. Lastly, multilevel models permit inference to a population of groups, treating sampled groups as a random sample from a larger population, unlike fixed effects models, which restrict inferences solely to the sampled groups. These benefits collectively enhance the accuracy, depth, and scope of analyses, particularly in understanding complex hierarchical data structures and their effects \cite{Rasbash_2023}.
